
\section{Experience}

\outerlist{

\entrybig
	{\textbf{Siemens}}{Kitchener, ON, Canada}
	{Machine Learning \& Algorithms Engineering Intern}{May 2022 - Aug 2022}
\innerlist{
	\entryextra{Integrated software tools and IoT infrastructure with machine learning to create scale-able real-time intelligent applications.}
	\entryextra{Utilized \textbf{TensorFlow} and \textbf{Keras} in Python with a LSTM model architecture to develop a machine learning classifier.}
	\entryextra{Leveraged software tools \& libraries such as MLflow, \textbf{Pandas} and \textbf{Docker} in machine learning operations \& data engineering.}
	\entryextra{Created publisher and subscriber agents with Docker using \textbf{MQTT} and \textbf{Kafka} protocols to enable edge processing.}
}

\entrybig
	{\textbf{Athos}}{Redwood City, CA, USA}
	{Embedded Engineering Intern}{Jan 2021 - April 2021}
\innerlist{
	\entryextra{Developed firmware for an NRF and STM SoC using \textbf{C} with The Zephyr Project \textbf{RTOS} and \textbf{Python} for scripts and testing.}
	\entryextra{Utilized embedded tools such as \textbf{GDB}, \textbf{Jlink}, \textbf{Altium} and \textbf{Oscilloscopes} for development and debugging. }
	\entryextra{Developed an IMU, Magnetometer and digital signal processing driver using CMSIS and custom sensor APIs. }
	\entryextra{Implemented a firmware architecture for automated PCBA testing of peripherals such as BLE, SPI, I2C, GPIO, PWM and UART.}
}

\entrybig
	{\textbf{Athos}}{Redwood City, CA, USA}
	{Software Engineering Intern}{Sept 2021 - Dec 2021}
\innerlist{
    \entryextra{Integrated and developed component and system tests into a \textbf{Jenkins} \textbf{CICD} and End-to-End testing pipeline.}
    \entryextra{Utilized \textbf{Robot Framework} to develop automated End-to-End tests involving Python, iOS, Redis, and C components. }
    \entryextra{Developed UI tests for an iOS mobile app using the Xcode UI testing (XCUI) testing framework in \textbf{Swift}.}
}

\entrybig
	{\textbf{IntelliCulture}}{Kitchener, ON, Canada}
	{Software Engineering Intern (Co-op \& Part-time)}{May 2020 - Present}
\innerlist{
    \entryextra{Leading development of the back-end infrastructure and data platform for core products and internal development.}
    \entryextra{Leveraged \textbf{OpenCV}, Jupyter Lab and \textbf{Python} to develop image object edge detection algorithms and processing.}
	\entryextra{Maintaining and improving \textbf{NodeJs}, Python, \textbf{Bash Scripting}, Fauna DB, \textbf{Docker}, and \textbf{Jenkins} technology stack.}
}

\entrybig
	{\textbf{Geotab}}{Kitchener, ON, Canada}
	{Automotive R\&D Engineering Intern}{Sept 2019 - Dec 2019}
\innerlist{
	\entryextra{Performed R\&D with \textbf{hardware} and \textbf{firmware} for IoT devices within a embedded development environment.}
	\entryextra{Designed a custom \textbf{PCB} for hardware testing using \textbf{Altium} to develop the schematic, board layout and component libraries.}
	\entryextra{Engaged in rapid prototyping utilizing \textbf{Arduino} for quick development while reverse engineering various PCB's and devices.}
}

}
